GRN inference in multiple species

### 2015-04-27 paper1.tex
hi

We also implement MCP [IS THIS MODIFIED TO BE L2 like at the origin?]

@@

As in [Fan Li], we use solve using iterative local quadratic approximation. Specifically,

\begin{equation}
\begin{array}{l}
\beta^S(t)\text{ is the network on iteration } t
\\
\text{for each fused  } B^{S_1}_{g,k} \approx B^{S_2}_{h,l}  \text{ we define } 
\\
\theta(0)=0
\\
\theta(t) = \vert B^{S_1}_{g,k} - B^{S_2}_{h,l} \vert
\\
\text{and introduce a fusion constraint } \lambda = \frac{p'(\theta(t))}{2\theta(t)} 
\\
\beta^S(t+1) \text{ is obtained by fitting the ridge-fused model with fusion constraints given by the above }\lambda s
\end{array}
\end{equation}

@@

@@

>>>>

We also implement MCP:

@@

As in [Fan Li], we use solve using iterative local quadratic approximation.

Specifically, $\beta^S(t)$ is the network on iteration $t$.

\begin{equation}
\begin{array}{l}
\text{for each fused  } B^{S_1}_{g,k} \approx B^{S_2}_{h,l}  \text{ we define: } 
\\
\theta(0)=0
\\
\theta(t) = \vert B^{S_1}_{g,k} - B^{S_2}_{h,l} \vert
\\
\text{and introduce a fusion constraint } \lambda = \frac{p'(\theta(t))}{2\theta(t)} 
\\
\end{array}
\end{equation}

$\beta^S(t+1)$ is obtained by fitting the ridge-fused model with fusion constraints given by the above $\lambda_S$. This is nice because all our penalties can be treated as L2 and therefore retain the properties of ridge regression.

@@

\subsection{Optimization and model selection}

@@

\section{Results}

\subsection{Fusing similar network has the same effect as increasing the number of experimental conditions}
When the sample size of gene expression increases, the performance

\subsection{SCAD successfully identifies and unfuses 'neofunctionalized' genes}
